---
title: "cluster-analysis"
date: "`r Sys.time()`"
author: "Rick Gilmore"
output:
  github_document:
    html_preview: true
    toc: true
    toc_depth: 3
  html_notebook: default
  pdf_document:
    toc: true
    toc_depth: 3
---

## Purpose

This notebook documents the process of evaluating the clusters within the PEEP-II (or peep2) ratings data.

```{r preliminaries}
library(tidyverse)
library(stringr)
```

## Copy data and import

The behavioral data are currently (2017-06-20-15:02) stored in `~/Box\ Sync/b-peep-project\ Shared/PEEP2\ data/PEEP2\ Home\ visit\ behavioural\ data/` as a set of `*.csv` files.

```{r import-data-test}
peep2.data.dir <- "~/Box\ Sync/b-peep-project\ Shared/PEEP2\ data/PEEP2\ Home\ visit\ behavioural\ data/"

# List files and open one for inspection
peep2.flist <- list.files(path = peep2.data.dir, pattern = "\\.csv$", full.names = TRUE)
peep2.test.df <- read.csv(file = peep2.flist[1])
peep2.df.list <- lapply(peep2.flist, read.csv)
peep2.df <- Reduce(function(x,y) merge(x,y, all =TRUE), peep2.df.list)

# Pick character ranges by hand
peep2.df$target_prosody <- str_sub(peep2.df$snd_file, 18, 20)
peep2.df$script_name <- str_sub(peep2.df$snd_file, 22, 24)
peep2.df$script_variation <- str_sub(peep2.df$snd_file, 26, 26)

# Trim sound file names for easier viewing
peep2.df$snd_file <- str_sub(peep2.df$snd_file, 14, 26)
```

## Hierarchical clustering

There are too many exemplars to do a full cluster analysis with `hclust()`, so I have to choose a subset. Perhaps we should look at the clusters on a participant-by-participant basis.

Let's create a function to create a cluster fit from the raw score data see <https://stackoverflow.com/questions/20343398/how-to-use-hclust-as-function-call-in-r>.

```{r define-hclustfunc}
hclustfunc <- function(x, method = "complete", dmeth = "euclidean") {    
    hclust(dist(x, method = dmeth), method = method)
}
```

```{r subset-filter-by-participant}
this_fam = 1
peep2.df %>%
  filter(fam_id == this_fam) -> this_fam.df

this_fam.df %>%
  select(sad_rating, happy_rating, angry_rating, how_feel) %>%
  hclustfunc() -> fit

plot(fit, labels = this_fam.df$target_prosody)
```

## Multidimensional scaling

```{r mds-try-1}
# select ratings
d <-dist(this_fam.df[,7:10])
mds_fit <- cmdscale(d, eig=TRUE, k=2)

x <- mds_fit$points[,1]
y <- mds_fit$points[,2]
plot(x, y, xlab="Coordinate 1", ylab="Coordinate 2",  main="Metric	MDS",	type="n")
text(x, y, labels = this_fam.df[,'target_prosody'], cex=.7)
```

Let's try a ggplot version.

```{r mds-ggplot-try-1}
# Make new data frame
mds.df <- data.frame(x = mds_fit$points[,1],
                     y = mds_fit$points[,2],
                     target_prosody = this_fam.df$target_prosody,
                     script_name <- this_fam.df$script_name,
    script_variation = this_fam.df$script_variation)

mds.df %>%
  ggplot() +
  aes(x = x, y = y, color = target_prosody) +
  geom_point()
```

```{r mds-ggplot-try-2}
# Try with another family
this_fam = 2
peep2.df %>%
  filter(fam_id == this_fam) -> this_fam.df
# select ratings (not scared)
d <- dist(this_fam.df[,7:10])
mds_fit <- cmdscale(d, eig=TRUE, k=2)
mds.df <- data.frame(x = mds_fit$points[,1],
                     y = mds_fit$points[,2],
                     target_prosody = this_fam.df$target_prosody,
                     script_name <- this_fam.df$script_name,
    script_variation = this_fam.df$script_variation)

mds.df %>%
  ggplot() +
  aes(x = x, y = y, color = target_prosody) +
  geom_point() +
  facet_grid(. ~ script_variation)
```

Let's try a version for this subject adding back in the `scared.rating`.

```{r, mds-ggplot-try-3}
this_fam = 2
peep2.df %>%
  filter(fam_id == this_fam) -> this_fam.df

d <- dist(this_fam.df[,c('happy_rating',
                         'angry_rating',
                         'sad_rating',
                         'how_feel',
                         'scared.rating')])
mds_fit <- cmdscale(d, eig=TRUE, k=2)
mds.df <- data.frame(x = mds_fit$points[,1],
                     y = mds_fit$points[,2],
                     target_prosody = this_fam.df$target_prosody,
                     script_name <- this_fam.df$script_name,
    script_variation = this_fam.df$script_variation)

mds.df %>%
  ggplot() +
  aes(x = x, y = y, color = target_prosody) +
  geom_point() +
  facet_grid(. ~ script_variation)
```

## K-means

```{r k-means-try-1}

this_fam = 2
peep2.df %>%
  filter(fam_id == this_fam) -> this_fam.df

ratings <- this_fam.df[,c('happy_rating',
                         'angry_rating',
                         'sad_rating',
                         'how_feel',
                         'scared.rating')]

set.seed(20)
ratings_cluster <- kmeans(this_fam.df[,c('happy_rating',
                         'angry_rating',
                         'sad_rating',
                         'how_feel',
                         'scared.rating')], 
                         centers = 4, 
                         nstart = 20)
ratings_cluster

table(ratings_cluster$cluster, this_fam.df$target_prosody)

# this_fam.df %>% 
#   ggplot() +
#   aes(happy_rating, how_feel, color = as.factor(ratings_cluster$cluster)) + 
#   geom_point()
```

Note that the angry and happy prosodies seem to cluster more readily than do the neutral and sad.