---
title: "PEEP II Acoustics Data Gathering"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_notebook:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_paged: true
    code_folding: show
---

# Background/Purpose

This notebook describes how to gather the PEEP-II acoustics data, including the formats of data files and fields.

# Set-up

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

pkg_list <- c("tidyverse", "ggplot2", "R.matlab")
lapply(pkg_list, library, quietly = TRUE, character.only = TRUE)
```

# Gather

## Explore and document directory structure

The PEEP II acoustics data are stored in `~/Box Sync/b-peep-project Shared/PEEP2 acoustics/`. 

```{r}
acoustics_dir <- "~/Box Sync/b-peep-project Shared/PEEP2 acoustics/"
dir(acoustics_dir)
```

There are separate directories for the individual participants, e.g. `001`.

Peter Moriarity recalls that `015_original` might have been recorded at 96,000 Hz (48,000 Hz was the standard for the rest). This participant may also have required down-sampling/editing to fit within the 10 s/utterance limit.

The contents of the `001` directory is as follows.

```{r}
dir(paste0(acoustics_dir, "/001"))
```

I presume that we'll want the `rmsnorm` data, but will check on that with Peter Moriarty.

```{r}
dir(paste0(acoustics_dir, "/001/rmsnorm"))
```

These look like the normed audio files.
Investigating the `data` subfolder, I find the acoustic ratings.

```{r}
dir(paste0(acoustics_dir, "/001/data"))
```

Examining the `F0` directory shows the following:

```{r}
dir(paste0(acoustics_dir, "/001/data/F0"))
```
 
Drilling down into the F0 directory, we see the following:

```{r}
list.files(paste0(acoustics_dir, "/001/data/F0/F0/mean"))
```

## Open `F0.mat` file

There is a MATLAB file `F0.mat` with the raw data.
To attempt to read it, I installed the `R.matlab` package via `install.packages("R.matlab")`.

```{r read-F0-matlab}
f0_001 <- R.matlab::readMat(paste0(acoustics_dir, "/001/data/F0/F0/mean/F0.mat"))
f0_001
```

Use the `str()` function to summarize the details.

```{r}
str(f0_001)
```

This is an 8x4x4 array. 
The dimensions are as follows: 8 scripts \{chk-a, chk-b, din-a, din-b, hlp-a, hlp-b, tlk-a, tlk-b\} x 4 emotions \{ang, hap, neu, sad\}, x 4 utterances/script. 

For now, let's open one of the other acoustics data files.


```{r}
dir(paste0(acoustics_dir, "/001/data"))
```

Let's try the harmonic to noise ratio or HNR.

## Opening HNR files

```{r}
dir(paste0(acoustics_dir, "/001/data/HNR"))
```

```{r}
dir(paste0(acoustics_dir, "/001/data/HNR/HNR"))
```

Let's examine `MEAN`.

```{r}
dir(paste0(acoustics_dir, "/001/data/HNR/HNR/MEAN"))
```

This is a `.mat` file we can open.

```{r}
HNR_mean_001 <- R.matlab::readMat(paste0(acoustics_dir, "/001/data/HNR/HNR/MEAN/HNR.mat"))
HNR_mean_001
str(HNR_mean_001)
```

This also has an 8x4x4 array structure.

# Steps toward a reproducible import scheme

## Exploring how to flatten these arrays

Let's create a test array with the same dimensionality, but named, so that we can explore how to properly flatten it.

```{r}
acoustics_test <- array(data = 1:(8*4*4), dim = c(8,4,4))
scr <- rep(rep(c("chk-a", "chk-b", "din-a", "din-b", "hlp-a", "hlp-b", "tlk-a", "tlk-b"), times = 4), times = 4)
emo <- rep(rep(c("ang", "hap", "neu", "sad"), each = 8), times = 4)
utt <- rep(1:4, each = 32)
df <- as.data.frame(acoustics_test)
df
```

So, I need to create one variable from the columns `V1` to `V16`.

```{r}
v <- NULL
for (i in 1:16) {
  v <- c(v, df[,i])
}
v
```

Now, I put the pieces together to form a data frame.

```{r}
acoustics_df <- data.frame(measure = v, script = scr, prosody = emo, utterance = utt)
```

## Making an import function

A function that should work on the `F0` (mean) and `HNR` files is as follows:

```{r define-import-function}
extract_acoustics_dat <- function(fn) {
  ac_mat <- R.matlab::readMat(fn)
  
  # Check dimensionality  
  # if ((!dim(ac_mat)[1] == 8) | 
  #   (!dim(ac_mat)[2] == 4) |
  #   (!dim(ac_mat)[3] == 4)) {
  #   stop("File is not 8x4x4 in dimension")
  # }
  
  # Convert to data frame
  ac_dat <- as.data.frame(ac_mat$data)
  
  # Convert data to 1D array
  v <- NULL
  for (i in 1:16) {
    v <- c(v, ac_dat[,i])
  }
  
  # Define values for nominal variables
  scr <- rep(rep(c("chk-a", "chk-b", "din-a", "din-b", 
                   "hlp-a", "hlp-b", "tlk-a", "tlk-b"), times = 4), times = 4)
  emo <- rep(rep(c("ang", "hap", "neu", "sad"), each = 8), times = 4)
  utt <- rep(1:4, each = 32)
  
  # Assemble data frame and return
  data.frame(data.frame(measure = v, script = scr, 
                        prosody = emo, utterance = utt))
             
}
```

Test the function.

```{r test-import-function}
extract_acoustics_dat(fn = paste0(acoustics_dir, "/001/data/F0/F0/mean/F0.mat"))
```

It makes more sense to sort by utterance within script.

```{r}
d <- extract_acoustics_dat(fn = paste0(acoustics_dir, "/001/data/F0/F0/mean/F0.mat"))
d %>% dplyr::arrange(script, prosody, utterance)
```

Let's incorporate this into the function.

```{r update-extract-function}
extract_matlab_acoustics_dat <- function(fn) {
  ac_mat <- R.matlab::readMat(fn)
  
  # Check dimensionality  
  # if ((!dim(ac_mat)[1] == 8) | 
  #   (!dim(ac_mat)[2] == 4) |
  #   (!dim(ac_mat)[3] == 4)) {
  #   stop("File is not 8x4x4 in dimension")
  # }
  
  # Convert to data frame
  ac_dat <- as.data.frame(ac_mat$data)
  
  # Convert data to 1D array
  v <- NULL
  for (i in 1:16) {
    v <- c(v, ac_dat[,i])
  }
  
  # Define values for nominal variables
  scr <- rep(rep(c("chk-a", "chk-b", "din-a", "din-b", 
                   "hlp-a", "hlp-b", "tlk-a", "tlk-b"), times = 4), times = 4)
  emo <- rep(rep(c("ang", "hap", "neu", "sad"), each = 8), times = 4)
  utt <- rep(1:4, each = 32)
  
  # Assemble data frame and return
  df <- data.frame(data.frame(measure = v, script = scr, 
                        prosody = emo, utterance = utt))
  dplyr::arrange(df, script, prosody, utterance)          
}

extract_matlab_acoustics_dat(fn = paste0(acoustics_dir, "/001/data/F0/F0/mean/F0.mat"))
```

That looks good.
An improvement would be to provide the measure name.

```{r}
extract_matlab_acoustics_dat_2 <- function(fn, measure_nm = "measure") {
  ac_mat <- R.matlab::readMat(fn)
  
  # Check dimensionality  
  # if ((!dim(ac_mat)[1] == 8) | 
  #   (!dim(ac_mat)[2] == 4) |
  #   (!dim(ac_mat)[3] == 4)) {
  #   stop("File is not 8x4x4 in dimension")
  # }
  
  # Convert to data frame
  ac_dat <- as.data.frame(ac_mat$data)
  
  # Convert data to 1D array
  v <- NULL
  for (i in 1:16) {
    v <- c(v, ac_dat[,i])
  }
  
  # Define values for nominal variables
  scr <- rep(rep(c("chk-a", "chk-b", "din-a", "din-b", 
                   "hlp-a", "hlp-b", "tlk-a", "tlk-b"), times = 4), times = 4)
  emo <- rep(rep(c("ang", "hap", "neu", "sad"), each = 8), times = 4)
  utt <- rep(1:4, each = 32)
  
  # Assemble data frame and return
  df <- data.frame(data.frame(measure = v, script = scr, 
                        prosody = emo, utterance = utt))
  # Rename measure (hacky)
  df[measure_nm] <- df$measure
  df <- dplyr::select(df, -measure)
  
  dplyr::arrange(df, script, prosody, utterance)
}

extract_matlab_acoustics_dat_2(fn = paste0(acoustics_dir, "/001/data/F0/F0/mean/F0.mat"), "F0_mean")

```
 
 This all works, except for the dimension checking.
 I will put this into an R file (`R/gather_clean_acoustics.R`) for sourcing.
 
## Plot `F0_mean` just for fun
 
```{r plot-001-f0-mean}
f0_001_df <- extract_matlab_acoustics_dat_2(fn = paste0(acoustics_dir, "/001/data/F0/F0/mean/F0.mat"), "F0_mean")

f0_001_df %>%
  ggplot(.) +
  aes(utterance, F0_mean, color = script) +
  geom_line() +
  facet_grid(. ~ prosody) +
  ylab("Mean F0 (Hz)") +
  ggtitle("Participant 001: F0 mean by prosody and utterance")
```
 
## Parse `script` into `script` and `order` variables

The ratings data have separate `script` and `order` variables.

```{r}
f0_001_df %>%
  tidyr::separate(., script, into = c("script", "order"))
```

## Import and test functions from `R/gather_clean_acoustics.R`

```{r source-gather-clean}
source("R/gather_clean_acoustics.R")
```

Now run `test_gather_clean_acoustics()` with the default parameters (`fam_id` == "001" and the "F0_mean" variable).

```{r run-test-gather}
test_gather_clean_acoustics()
```

Try it with the `HNR_mean` and a different participant.

```{r run-test-gather-non-default}
test_gather_clean_acoustics(this_fam = "002", this_measure_nm = "HNR_mean")
```

# Next steps

1. ~~Parse the `script` variable into separate `script` and `order` variables analogous to the ratings data.~~
    - 2019-08-01: Completed.
    
2. Create functions to recursively scour the acoustics data structure and generate files for each measure for each participant.
    - 2019-08-01: Partially done, see `R/gather_clean_acoustics.R`.
    
3. Save the files for each participant with a sensible naming scheme like `001_F0_mean.csv` or `001_HNR.csv`.

4. Create combined files across participants by measure.

5. Create summary (mean value across utterances) data for each recording as this is the data in the JECP paper. Focus on the `F0_mean`, standard deviation of F0, and speech rate variables. Confirm with Peter how to calculate standard deviation of F0 (by file/recording SD?), and speech rate.
