---
title: "peep-II-ratings-models"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_paged: true
    code_folding: hide
---

# Purpose

1. To explore a series of statistical models of PEEP-II ratings data at the *individual* level.

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pkg_list <- c("googlesheets", "googledrive", "tidyverse", "ggplot2", "ggmosaic")
lapply(pkg_list, library, quietly = TRUE, character.only = TRUE)
```

# Import data

```{r import-data, message=FALSE}
source("R/gather_clean_ratings.R")
source("R/gather_clean_demog.R")

ratings <- clean_peep_II_ratings(gather_peep_II_ratings())
demog <- clean_peep_II_demog(gather_peep_II_demo())
ratings_demog <- dplyr::left_join(demog, ratings, by = "fam_id")
```

Based on the <peep-II-qa.html> findings, we sould consider dropping 019 and 032 from analysis of the `*_rating` data.
These participants were not tested on the full set of ratings.
An alternative would be to select one of the two (identical) runs.
I'm going to drop 019 and 032 for now.

```{r}
ratings_sub <- ratings_demog %>%
  filter(!(fam_id %in% c(19, 32)))
```

Similarly, if we want to examine the `know_speaker` variable, we have to worry about 001 and 003.
I'm not evaluating that variable now, so we'll keep 001 and 003.

# Set-up nested tibble

Here, I am following the examples in Chapter 20 of the R for Data Science book.

```{r}
by_fam <- ratings_sub %>%
  group_by(fam_id) %>%
  nest()
```

Now, we can try the by-participant modeling!

```{r}
happy_model <- function(df) {
  aov(happy_rating ~ prosody*spkr_fam*script, data = df)
}

angry_model <- function(df) {
  aov(angry_rating ~ prosody*spkr_fam*script, data = df)
}

sad_model <- function(df) {
  aov(sad_rating ~ prosody*spkr_fam*script, data = df)
}
  
scared_model <- function(df) {
  aov(scared_rating ~ prosody*spkr_fam*script, data = df)
}

how_feel_model <- function(df) {
  aov(how_feel ~ prosody*spkr_fam*script, data = df)
}

by_fam_mods <- by_fam %>%
  mutate(., 
         hap_model = purrr::map(data, happy_model),
         hap_resids = purrr::map2(data, hap_model, modelr::add_residuals),
         ang_model = purrr::map(data, angry_model),
         ang_resids = purrr::map2(data, ang_model, modelr::add_residuals),
         sad_model = purrr::map(data, sad_model),
         sad_resids = purrr::map2(data, sad_model, modelr::add_residuals))
```
