---
title: "PEEP II Ratings Visualization for Individual"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_paged: true
    code_folding: hide
  github_document:
    html_preview: true
    toc: true
    toc_depth: 3
    number_sections: true
params:
  db_account: rogilmore@psu.edu
---

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
```

# Purpose

This report generates some PEEP-II ratings data visualizations relevant for individual participants.

# Import data

The cleaned data can be found at `data/csv/peep-II-ratings-demog.csv`.

```{r import-ratings-demo}
ratings_demo <- read_csv('data/csv/peep-II-ratings-demog.csv')
```

# Preparing to visualize

## Overall strategy

For the *JECP* manuscript, we focus on intensity ratings for the target prosody.
That is, we compare a child's `angry_rating` of recordings intended by the speaker to convey anger, and so forth.
We ask:

1. Do children rate their own mothers' voices as more intense than unfamiliar mothers' voices?
2. Do acoustic properties account for children's intensity ratings?

We are not especially concerned here with differences by `script`, `run`, or `order` although these may occur.
Since we did not ask children to rate 'how un-emotional or neutral' a recording was, we drop consideration of ratings of `neu` or non-emotional prosody.

## Create unitary `intensity` variable

Create a single `intensity_rating` variable from the \{happy, angry, sad\}_rating variables and an `emotion_rated` variable to indicate the emotion the rater was evaluating at the time.

```{r create-intensity-df}
intensity <- ratings_demo %>%
  tidyr::gather(., key = "emotion_rated", value = "intensity_rating", `happy_rating`:`sad_rating`) %>%
  dplyr::select_all(.) %>%
  dplyr::mutate(., emotion_rated = stringr::str_sub(stringr::str_extract(emotion_rated, 'happy|angry|sad'), 1, 3))
str(intensity)
```

Next, we select the intensity ratings for circumstances when the `emotion_rated` equals the `prosody`.

```{r filter-intensity-ratings-for-same-emo-as-target}
intensity <- intensity %>%
  filter(., emotion_rated == prosody)
```

Now we can move on to plotting.

# Group plots

We'll start with group plots since we've done these before.

## Histogram of ratings by speaker and prosody

```{r plot-bar-intensity-by-prosody-speaker}
intensity <- intensity %>%
  filter(intensity_rating != 0) 

intensity %>%
  ggplot(.) +
  aes(x = intensity_rating, fill = speaker_familiarity) +
  facet_grid(prosody ~ .) +
  geom_bar(position = "dodge")
```

The grouped plot seems to work, so let's divide this up into panels to see finer-grained results.

## Histogram by script and target prosody

```{r plot-bar-intensity-by-prosody-script-speaker}
intensity <- intensity %>%
  filter(intensity_rating != 0) 

intensity %>%
  ggplot(.) +
  aes(x = intensity_rating, fill = speaker_familiarity) +
  facet_grid(prosody ~ script) +
  geom_bar(position = "dodge")
```

There are some differences by script and emotion.
The checkbook `chk` script shows flat ratings for happiness `hap`.
The `sad` prosodies are rated less intensely sad by children, regardless of the script.
The familiar `fam` speaker (mother) is generally rated as more intensely angry and happy across most of the scripts.

# Individual level plots

To really understand what's happening, we should look at plots by individuals.

```{r}
fam_ids <- unique(intensity$fam_id)
```

## Family 1 | `r paste0(1, ' of ', length(fam_ids))`

There are two different script types, `a` and `b` for each script.
So, there should be four data points in each of the panels above for each participant.
Here's an attempt to visualize these for a single participant.

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == 1) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
```

If raters *consistently* rated the familiar speaker as more intensely emotional, then the slope of these paired lines should be downward to the right.
We see the expected pattern in five conditions: `hlp` + `ang`, `tlk` + `hap`, and to a lesser extent in `tlk` + `ang`, `chk` + `hap`, and `din` + `sad`.
Several (4) conditions are a wash: `chk` + `ang`, `din` + `ang`, `din` + `hap`, `hlp` + `hap`.
Three show the *opposite* pattern: `hlp` + `sad`, `tlk` + `sad`, and less so `din` + `sad`.



```{r}
i = 2
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', 
                 fam_ids[i], ' | ', i, ' of ', length(fam_ids)))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```

## Family `r paste0('Family ', fam_ids[i], ' | ', i, ' of ', length(fam_ids))`

```{r}
intensity %>%
  filter(intensity_rating != 0,
         fam_id == fam_ids[i]) %>%
  ggplot(.) +
  aes(x = speaker_familiarity, y = intensity_rating, group = order) +
  facet_grid(prosody ~ script) +
  geom_point(aes(color = speaker_familiarity)) +
  geom_line(aes(linetype = order)) +
  scale_y_continuous(limits = c(1,4)) +
  ggtitle(paste0('Family ', fam_ids[i]))
i <- i + 1
```
