---
title: "PEEP II Ratings Acquire & Clean"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_paged: true
    code_folding: hide
params:
  db_account: rogilmore@psu.edu
  
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)

library(tidyverse)
library(R.matlab)
library(googlesheets)
```

This file uses the `tidyverse` and `R.matlab` packages.

# Purpose

1. Acquire behavioral ratings data for PEEP II study.
2. Acquire acoustic data for PEEP II study.
3. Acquire demographic data for PEEP II study.
4. Clean data files and merge into one dataset for analysis.

# Ratings data

## Acquire

As of 2019-06-20, ratings data are stored in a shared Box folder:

"~/Box\ Sync/b-peep-project\ Shared/PEEP2\ data/PEEP2\ Home\ visit\ behavioural\ data/"

```{r acquire-ratings}
data_dir <- "~/Box\ Sync/b-peep-project\ Shared/PEEP2\ data/PEEP2\ Home\ visit\ behavioural\ data/"

# List files and open one for inspection
flist <- list.files(path = data_dir, 
                          pattern = "\\.csv$", 
                          full.names = TRUE)
ratings_list <- lapply(flist, read.csv)
ratings <- Reduce(function(x,y) merge(x,y, all =TRUE), ratings_list)
```

## Clean

There are several cleaning tasks for these data:

1. Change `scared.rating` to `scared_rating` for consistency with other file names.
2. Parse `snd_file` so that the target prosody, e.g., `ang`, script, e.g, `chk`, and order, e.g., `a`, are separate columns.
3. Parse `snd_file` so that the speaker IDs can be turned into `fam` or `nov` codes indicating whether the mother or a novel mother is speaking.

```{r clean-ratings}
ratings <- ratings %>%
  rename(scared_rating = scared.rating)

# Parse group 1 = speaker, group 2 = prosody, group 3 = script, group 4 = order
snd_file_regex <- "([0-9]+)-([a-z]+)-([a-z]+)-([ab])"
snd_file_extract <- stringr::str_match(ratings$snd_file, snd_file_regex)

ratings <- ratings %>%
  mutate(speaker = snd_file_extract[,2],
         prosody = snd_file_extract[,3],
         script  = snd_file_extract[,4],
         order   = snd_file_extract[,5])
```

Finally, we create a `familiar` variable based on the speaker.

```{r familiar}
ratings <- ratings %>%
  mutate(familiar_bool = (fam_id == as.numeric(speaker)))

ratings$familiar <- factor(as.numeric(ratings$familiar_bool), labels = c("nov", "fam"))
```

# Acoustic data

## Acquire

The acoustic data are in a shared Box folder:

`~/Box\ Sync/b-peep-project Shared/PEEP2\ acoustics/`

There is a folder for each subject:

```{r list-acoustic-files}
acoustic_dir <- "~/Box\ Sync/b-peep-project Shared/PEEP2\ acoustics/" 
list.files(acoustic_dir)
```

Within each subject directory, there are subdirectories:

```{r}
list.files(paste0(acoustic_dir, "/001"))
```

The `data/` directory contains additional subdirectories:

```{r}
list.files(paste0(acoustic_dir, "/001/data"))
```

These concern the various acoustic measures.
Drilling down into the F0 directory, we see the following:

```{r}
list.files(paste0(acoustic_dir, "/001/data/F0/F0/mean"))
```

There is a MATLAB file with the raw data.
To attempt to read it, I installed the `R.matlab` package via `install.packages("R.matlab")`.

```{r read-F0-matlab}
f0_001 <- R.matlab::readMat(paste0(acoustic_dir, "/001/data/F0/F0/mean/F0.mat"))
f0_001
```

This is an 8x4x4 array. There were 4 scripts x 2 versions x 4 target prosodies. 
That gives $n=32$ exemplars.
Could the additional 4 data points refer to the F0 for each *utterance* within the exemplar, assuming that there are four utterances/script.
I'm stuck until I figure this out.

Once the meaning of the dimensions is clear, then it may be necessary to average the per-utterance values to create a per/script mean and SD, as these were the variables we used in the JECP manuscript.

# Demographic data

## Acquire

The demographic data for the study are stored in a Google sheet.
This requires using the `googlesheets` library.

*Note*: When run using `rmarkdown::render()`, the `googlesheets` commands must authenticate to Google in order to grant a user access to the sheet.
This means that the user must authenticate to Google *outside* of the typical rendering workflow.

Note also that family 007 was apparently dropped.
I do not know why, but there are no ratings data for 007 either, so everything checks out.

```{r import-demographics-from-Google}
dropped_subs <- "007"
demog_sheet <- gs_title("PEEP II Data Management")

demog_full <- demog_sheet %>%
  gs_read(ws = 1) %>%  
  filter(`Completed/Scheduled Visit 2` == "completed",
         `Completed/Scheduled EAR Day` == "completed",
         `Completed/Scheduled Visit 3` == "completed",
         !(`ID Number` %in% dropped_subs))

str(demog_full)
```

There are many more variables in the spreadsheet than we need for this analysis.
We'll trim it to the most important ones for our current purposes.

```{r demog-trim}
demog <- demog_full %>%
  select(`ID Number`, `Two Parent Family?`, 
         `Mother Gender`,`Mother Race`, `Mother Latina?`,
         `Other Parent Gender`, `Other Parent Race`,
         `Other Parent Latino?`,
         `Target Child DOB`, `Target Child Gender`,
         `Target Child Race`, `Target Child Latino?`)
```

## Clean

Our goals for cleaning these data are as follows:

1. Consider renaming the variables to make them shorter, lower case, and consistent with the naming scheme used for the ratings data.
2. Calculate an age-at-test variable for the target child.

```{r clean-demog}
demog <- demog %>%
  rename(two_parent_fam = `Two Parent Family?`,
         mother_gender = `Mother Gender`,
         mother_race = `Mother Race`,
         mother_latinx = `Mother Latina?`,
         other_gender = `Other Parent Gender`,
         other_race = `Other Parent Race`,
         other_latinx = `Other Parent Latino?`,
         child_dob = `Target Child DOB`,
         child_gender = `Target Child Gender`,
         child_race = `Target Child Race`,
         child_latinx = `Target Child Latino?`) %>%
  mutate(fam_id = as.numeric(`ID Number`))
```

In order to calculate the age-at-test, I will need to import the test date for Visit 1 from sheet 3, 'Visit 1'.

```{r import-visit-1}
visit_1 <- gs_read(ss = demog_sheet, ws = 3)

visit_1 <- visit_1 %>%
  select(`Subject ID`, `Child Age at Visit (years, months)`)
```

Now, we can drop the participants who aren't in the sample of ratings, and normalize the age variable.

```{r select-participants-with-ratings}
participants_with_ratings <- unique(ratings$fam_id)

visit_1 <- visit_1 %>%
  filter(., as.numeric(`Subject ID`) %in% participants_with_ratings) %>%
  rename(., child_yrs = `Child Age at Visit (years, months)`) %>%
  mutate(., fam_id = as.numeric(`Subject ID`))
```

# Merge

## Ratings with demographics

Since I am stymied on the acoustics measures, let's merge the data we have.

```{r}
ratings_demo <- left_join(ratings, demog, by = "fam_id")
ratings_demo <- left_join(ratings_demo, visit_1, by = "fam_id")

# Now drop duplicate variables for ID and DOB
ratings_demo <- ratings_demo %>%
  select(-child_dob, -`ID Number`, -`Subject ID`)
str(ratings_demo)
```

There is some minor duplication.