---
title: "PEEP II Ratings & Acoustics"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    df_paged: true
    code_folding: show
params:
  db_account: rogilmore@psu.edu
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)

library(tidyverse)
library(ggplot2)
library(databraryapi)
```

# Purpose

1. To create a reproducible data cleaning and visualization pipeline.
2. To visualize the PEEP-II ratings and acoustic data.
3. To conduct confirmatory and exploratory analyses on these data.

# Data acquisition

## Import locally

The data are in `data/csv/long_speaker_acous_ratings_6.14.19.csv'.

```{r import-data-locally}
ratings_acoustics <- readr::read_csv("data/csv/long_speaker_acous_ratings_6.14.19.csv")
```

## Import from Databrary

This is not working yet.

```{r}
peep_II_vol <- 339
```

# Clean

## Inspect

```{r inspect}
str(ratings_acoustics)
```

`Subject` is an integer. Does it correspond to the `Participant ID`?

```{r}
unique(ratings_acoustics$Subject)
length(unique(ratings_acoustics$Subject))
```

Yes, it appears to be the case that `Subject` == `Participant ID`.
This corresponds to the `session_name` variable in the Databrary volume.
The Databrary volume (https://nyu.databrary.org/volume/339) only has recordings up through participant 53, however.

## Add demographic data

We can add demographic data by merging the `ratings_acoustics` file with the Databrary spreadsheet.

```{r load-databrary-spreadsheet}
# Login required
databraryapi::login_db(email = params$db_account)

# Download session CSV
vol_39_demo <- databraryapi::download_session_csv(vol_id = peep_II_vol)
str(vol_39_demo)
```

The `session_name` variable seems to correspond with the dyad's participant number, as deduced previously.

```{r clean-databary-demo-data}
vol_39_clean <- vol_39_demo %>%
  dplyr::filter(!is.na(session_name)) %>% # drop materials
  dplyr::select(-participant1.birthdate, -participant2.birthdate) %>% # Birthdates
  dplyr::select(session_name,
                participant1.gender, participant1.race, participant1.ethnicity,
                participant2.race, participant2.ethnicity) %>%
  dplyr::rename(child_gender = participant1.gender, 
                child_race = participant1.race,
                child_ethnicity = participant1.ethnicity,
                mother_race = participant2.race,
                mother_ethnicity = participant2.ethnicity)
```

Now, we merge the ratings data with the demographic data.

```{r merge-ratings-demo}
ratings_acoustics_all <- dplyr::left_join(ratings_acoustics, vol_39_clean, by = c("Subject" = "session_name"))
```

## Refactor to make names explicit

1. Speaker is in \{0,1\}. Which is familiar and which novel?
2. Prosody is in \{1,2,3\}. How do these map to happy, angry, sad?
I suspect that 1=happy, 2=angry, and 3=sad.
3. Units of F0_mean must be Hz. So must F0_SD. What about speech rate?

## Add back or acquire script and order variables

# Visualizations

## Intensity ratings by target prosody

Create a single variable from the \{Happy, Angry, Sad\}_Rating variables.

```{r}
ratings_acoustics_gathered <- ratings_acoustics_all %>%
  tidyr::gather(., key = "Prosody", value = "Intensity_Rating", 4:6) %>%
  dplyr::select_all() %>%
  dplyr::mutate(., Target_Prosody = stringr::str_extract(Prosody, 'Happy|Angry|Sad'))

str(ratings_acoustics_gathered)
```

### Intensity_Rating by Target_Prosody by Speaker

```{r plot-bar-intensity-by-prosody-speaker}
ratings_acoustics_gathered$Speaker <- factor(ratings_acoustics_gathered$Speaker)
ratings_acoustics_gathered <- ratings_acoustics_gathered %>%
  filter(Intensity_Rating != 0) 

ratings_acoustics_gathered %>%
  ggplot(.) +
  aes(x = Intensity_Rating, fill = Speaker) +
  facet_grid(Target_Prosody ~ .) +
  geom_bar(position = "dodge")
```

It looks like this is reverse-coded--1=4, etc.
Let's assume it is and transform it.

```{r}
ratings_acoustics_gathered$Intensity_Rating <- 5 - ratings_acoustics_gathered$Intensity_Rating
```


### Jitter plot of Intensity_Ratings by Target_Prosody by Speaker

```{r plot-jitter-intensity-by-prosody-by-speaker}
ratings_acoustics_gathered %>%
  filter(Intensity_Rating != 0) %>%
  ggplot(.) +
  aes(x = Target_Prosody, y = Intensity_Rating, color = Target_Prosody, group = Subject) +
  geom_point(position = "jitter", alpha = .2) +
  facet_grid(. ~ Speaker)
```

```{r anova-intensity-by-ratings-speaker}


```


## Differences between speakers

The difference between speakers in perceived intensity ratings should be on [-3,3].
We need to 'spread' the values to calculate this.
But we can't do it because the Speaker and Target_Prosody values aren't unique without the Script and Order variables.
